---
title: "Diskriminierung auf Twitter"
output: 
  html_document:
    theme: cosmo
urlcolor: black
linkcolor: black
---
```{r setup, echo=FALSE}
# Setup
knitr::opts_chunk$set(collapse = TRUE)
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(echo = FALSE) 
knitr::opts_chunk$set(warning = FALSE) 
knitr::opts_chunk$set(message = FALSE) 
knitr::opts_chunk$set(fig.pos = 'H')
```

```{r library, echo=FALSE}
rm(list = ls())


# Library
library(dplyr)
```

```{r data.import}
load("/Users/virginia/Desktop/Blogbeitrag/NR_SR_Jan_Okt_2019.RData")

# Variables in the data set
names(NR_SR_Jan_Okt_2019)
```
<style>
div.blue { background-color:#edeef0; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

Name: Virginia Wenger  
Matrikelnummer: 15-102-239  
E-Mail: [virginia.wenger@uzh.ch](mailto:virginia.wenger@uzh.ch)  

Seminar: Politischer Datenjournalismus (HS 2020)  
Leitung: Theresa Gessler, Fabrizio Gilardi, Alexandra Kohler  
Abgabedatum:  

</div>

## General differences between genders on Twitter

### Preparing the data
```{r}
### Reshuffle parties 
NR_SR_Jan_Okt_2019$Party_Short[NR_SR_Jan_Okt_2019$Party_Short=="JCVP"] <- "CVP"
NR_SR_Jan_Okt_2019$Party_Short[NR_SR_Jan_Okt_2019$Party_Short=="jf"] <- "FDP"
NR_SR_Jan_Okt_2019$Party_Short[NR_SR_Jan_Okt_2019$Party_Short=="jglp"] <- "glp"
NR_SR_Jan_Okt_2019$Party_Short[NR_SR_Jan_Okt_2019$Party_Short=="JG"] <- "Grüne"
NR_SR_Jan_Okt_2019$Party_Short[NR_SR_Jan_Okt_2019$Party_Short=="JUSO"] <- "SP"
NR_SR_Jan_Okt_2019$Party_Short[NR_SR_Jan_Okt_2019$Party_Short=="JSVP"] <- "SVP"

## Filter parties
data <- NR_SR_Jan_Okt_2019 %>% 
  filter(Party_Short %in% c("CVP", "FDP", "glp", "Grüne", "SP", "SVP")) 
```


### Number of users 
```{r}
# by gender
data %>% 
  filter(Gender %in% c("m", "f")) %>%
  group_by(Gender) %>%
  tally() %>%
  arrange(desc(n))

# by gender and party
data %>% 
  filter(Gender %in% c("m", "f")) %>%
  group_by(Gender, Party) %>%
  tally() %>%
  arrange(desc(n))

```

### Number of tweets by gender
```{r}

```

### Number of followers by gender
```{r}

```

### Number of retweets by gender
```{r}
# by gender

# by party and gender

# Who retweets whom?

## retweets of men by men

## retweets of men by women

## retweets of women by men

## retweets of women by women

```

### Number of mentions
```{r}
# mentions by gender

# mentions by gender and party

# Who mentions whom?

## mentions of men by men

## mentions of men by women

## mentions of women by men

## mentions of women by women

```

### Number of answers
```{r}

# Number of answers by gender

# Reply ratio

```

### Rhetorical share of the conversation
#### What are the candidates abilities to drive the conversation within the networks of people talking about them?

The rethorical share is thenumber of tweets from a candidate plus number of times a candidate was retweeted divided throutg the total number of tweets in the network.

$$ rethorical\; share  = - \frac {C_t + C_{rt}}{Total\; n}  $$
```{r}

```

### Centrality
```{r}

# Eigenvektor centrality (= linked to power)
## = how connected is a node to toher nodes in the network with the greatest connectivity?

```